\documentclass[BTech]{iittpdiss} 
\input{structurethesis}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page

\title{GRAPH MODEL SELECTION IN GAUSSIAN GRAPHICAL MODELS}
\firstauthor{Anshul Yadav}
\firstrollnumber{2017EE10565}


\supervisors{Prof. Sandeep Kumar}
\date{JANUARY 2021}
\department{\MakeUppercase{Electrical Engineering}}

%\nocite{*}
\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Declaration
%\include{FrontContents/declaration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
\include{FrontContents/certificate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
\acknowledgements

I express my deepest gratitude to my advisor Prof. Sandeep Kumar who helped me in shaping up the entire project and provided constant encouragement, guidance and motivation at every step. I learned a lot from him during the process and greatly benefitted from his immense knowledge and insights.

I express my heartfelt gratitude to my Professors who always encouraged free flow of thoughts and inspired me to pursue Machine Learning as a career. I would specially like to thank Prof. Prathosh A.P. for introducing me to the field in such an elegant manner. 

I would also like to thank all my friends who acted as a constant support of motivation and learning during my four years at IIT Delhi. We together had lots of fun and unforgettable memories. I would especially like to mention my wingmates Adarsh Shrivastava, Aman Tiwari, Anchit Tandon, Anurag Yadav, Ashwil Bhupesh, Ayush Jain, Bhargav Varshney, Mayank Bulkunde, Neel Patel and Nihar Patel with whom I have developed an everlasting bond.

Lastly, I am greatly indebted to my parents and my brother Aakash who encouraged me to pursue my dreams throughout my life and supported me through every thick and thin. This journey wouldn\rq{}t have been possible without them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
\include{FrontContents/abstract}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}
\listoffigures
\addcontentsline{toc}{chapter}{LIST OF FIGURES}
\listoftables
\addcontentsline{toc}{chapter}{LIST OF TABLES}

\end{singlespace}

%Glossary

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
\include{FrontContents/abbreviations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notation

\include{FrontContents/notation}


% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction.

\include{Chapters/Chapter1}
%Literature Review
\include{Chapters/Chapter2}
%Mathematical Background
\include{Chapters/Chapter3}
%Results and Discussion
\include{Chapters/Chapter4}
%Summary
\include{Chapters/Chapter5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices.
%\include{BackContents/appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.
\Urlmuskip=0mu plus 1mu\relax
\begin{singlespace}
  \bibliography{refs}
\end{singlespace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% List of papers



\end{document}
